Introduction to Structural Causal Models

### 2021-05-21 presentation_video.Rmd
presentation

# Example Intevention

```{r}

```

@@

- Nodes 
- Edges
- Parents/Ancestors/Descendents
- (Missing) Arrows

>>>>

# Example Intevention (1)
**Atomic Intervention**:

- by replacing function with a constant

$$C_1:= f_{c_1}(p,q) \rightarrow C_1:=600$$
$$C_2:= f_{c_2}(a,b)$$
$$E:=f_E(C_1,C_2,N_E)$$

# Example Intevention (2)

**Policy Intervention:**

- Intervention by replacing function with a different conditional probability

$$C_1:= f_{c_1}(p,q) \rightarrow C_1:=f(\pi)$$
$$C_2:= f_{c_2}(a,b)$$
$$E:=f_E(C_1,C_2,N_E)$$

@@

- No need to specify exact parametric shape
- highlight colliders 
- estimation back door criterion 
-
- Nodes 
- Edges
- Parents/Ancestors/Descendents
- (Missing) Arrows

# Difference Path Diagramm and Pearls Causal Diagrams
